---
title: "Data Cleaning"
author: "Fernando Hoces de la Guardia"
date: "7/30/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(shiny)
library(tidyverse)
library(stringdist)
```

### First: basic clean up  
- load data  
- clean some DOIs  
- rename the title of a reproduction  
- generate a variable that takes the same value for titles that sound similar  
- generate unique identifier for each reproduction  
- Identify the maximum number of claims and display items reproduced across all reproduction attempts



```{r 01-basic}
# load data
# clean some DOIs
# rename the title of a reproduction
# generate a variable that takes the same value for titles that sound similar
# generate unique identifier for each reproduction

df <- read_csv("all_reproductions_aug_15_2021.csv") %>%
    mutate(clean_doi = str_extract(
        S0_1Q1P1,
        regex("10\\.\\d{4,9}/[-._;()/:a-z0-9]+$",   #Explain regex
              ignore_case = T)
    )) %>%
    mutate(
        S0_1Q1P2 = ifelse(
            test = (
                S0_1Q1P2 == "[Fernando] Railroads of the Raj: Estimating the Impact of Transportation Infrastructure"
            ),
            yes = "Railroads of the Raj: Estimating the Impact of Transportation Infrastructure",
            no = S0_1Q1P2
        )
    ) %>%
    mutate(similar_title = phonetic(S0_1Q1P2)) 

claims_max <- df %>% select(contains("S1_3Q1C")) %>% names() %>% length()
di_max <- df %>% select(contains("S2_4iD")) %>% names() %>% length()

```


### Second: build specification data in long format 
- Select reproduction_id, clean_doi, title identifier, original title, summary of each claim and names of display items for each claim
- rename summary and DI names to be more self-explanatory and in preparation for reshape
- reshape from wide to long
- remove the prefix of the spec variable
- keep obs with non-missing display item names

```{r 02-spec}

#loading the data
df_spec <- df %>% filter(status == "submitted" | status == "abandoned") %>%
    select(
        country_code,
        reproduction_id,
        clean_doi,
        similar_title,
        S0_1Q1P2,                       #title
        contains("S1_3Q1C"),            #claims summary
        contains("S1_3Q5C1_r1c"),       #Name of display items for claim 1
        contains("S1_3Q5C2_r1c"),       #...
        contains("S1_3Q5C3_r1c"),
        contains("S1_3Q5C4_r1c"),
        contains("S1_3Q5C5_r1c"),
        contains("S1_3Q5C6_r1c"),
        contains("S1_3Q5C7_r1c")       #Name of display items for last claim 
    ) %>% 
  select(!( ends_with(c("c7", "c8", "c9") , ignore.case = FALSE) )) %>% 
    rename_at(.vars = paste0("S1_3Q1C", 1:claims_max),
              .funs = ~ paste0("desc_", 1:claims_max)) %>% 
    rename_at(.vars = paste0("S1_3Q5C", 1:claims_max, "_r1c1"),
              .funs = ~ paste0("diname.main_", 1:claims_max)) %>% 
    rename_at(.vars = paste0("S1_3Q5C", 1:claims_max, "_r1c2"),
              .funs = ~ paste0("diname.altspec1_", 1:claims_max)) %>% 
    rename_at(.vars = paste0("S1_3Q5C", 1:claims_max, "_r1c3"),
              .funs = ~ paste0("diname.altspec2_", 1:claims_max)) %>% 
    rename_at(.vars = paste0("S1_3Q5C", 1:claims_max, "_r1c4"),
              .funs = ~ paste0("diname.altspec3_", 1:claims_max)) %>% 
    rename_at(.vars = paste0("S1_3Q5C", 1:claims_max, "_r1c5"),
              .funs = ~ paste0("diname.altspec4_", 1:claims_max)) %>% 
    rename_at(.vars = paste0("S1_3Q5C", 1:claims_max, "_r1c6"),
              .funs = ~ paste0("diname.altspec5_", 1:claims_max)) %>% 
    pivot_longer(
        #reshape to long
        cols = !c(reproduction_id, clean_doi, similar_title, S0_1Q1P2, country_code),
        # do not modify: repro id, title id, title, claim summ
        names_to = c(".value", "claims"),
        names_sep = "_"
    ) %>% 
    filter(!is.na(desc)) %>% 
    pivot_longer(
        cols = !c(reproduction_id, clean_doi, similar_title, S0_1Q1P2, claims, desc, country_code),
        names_to = "spec", 
        values_to = "diname"    
    ) %>% 
    mutate(spec = substring(spec, 8)) %>% 
    filter(!is.na(diname)) 

```



### Third: build display item data and reshape to long and merge with spec data  
- starting from main data set (first step)
- rename di score vars and di name vars in preparation for reshaping
- merge specifications with di names

```{r 03-di-merge}
df_di  <- df %>%
    rename_at(.vars = paste0("S2_4Q4_2D", 1:di_max),
              .funs = ~ paste0("score_", 1:di_max)) %>% 
    rename_at(.vars = paste0("S2_4iD", 1:di_max),
              .funs = ~ paste0("diname_", 1:di_max)) %>% 
    select(reproduction_id, contains("diname_"), contains("score_") ) %>% 
    pivot_longer(#reshape to long
        cols = !reproduction_id,   # do not modify: repro id
        names_to = c(".value", "id"),
        names_sep = "_" ) %>%  
    select(-id) %>% 
    filter(!is.na(diname)) 


df_app <- left_join(df_spec, df_di, 
                    by = c("reproduction_id", "diname")) %>% 
    filter(!is.na(score)) %>% 
    arrange(similar_title, reproduction_id, claims)

```


### Fourth: compute statistics 


```{r 04-}

write.csv(df_app, file = "test.csv")

stat1 %>% ggplot(aes(x = paper_level)) + 
    geom_histogram(binwidth = 1, color="black", fill="gray") +
    labs(title = "Distribution of Reproduction Scores: Paper Level", 
         x = "Reproducibility Score", 
         y = "Count") +
    coord_cartesian(ylim =  c( 0, 5 )) +
    scale_x_continuous(breaks=1:10)


if (FALSE){
    # distribution of scores of all display items
    df_app %>% 
        group_by(similar_title, reproduction_id, claims, diname) %>%      #repro-claim-di level (min? max? median? it should not matter)
        summarize(claim_di_level = mean(score)) %>% 
        ggplot(aes(x = claim_di_level)) + 
        geom_histogram(binwidth = 0.5) +
        labs(title = "Distribution of Reproduction Scores: Display Items", 
             x = "Reproducibility Score", 
             y = "Count") 
    
    # distribution of scores of all claims
    df_claims <- df_app %>% 
        group_by(similar_title, reproduction_id, claims, diname) %>%      #repro-claim-di level (min? max? median? it should not matter)
        summarize(claim_di_level = mean(score)) %>% 
        ungroup(diname) %>% 
        summarise(claim_level = min(claim_di_level))
    n_claims <- dim(df_claims)[1]
    df_claims %>% 
        ggplot(aes(x = claim_level)) + 
        geom_histogram(binwidth = 0.5) +
        labs(title = "Distribution of Reproduction Scores: All Claims", 
             x = "Reproducibility Score", 
             y = "Count") +
        annotate(
            "text",
            x = 1.7 * min(df_claims$claim_level) ,
            y = 15,
            label = paste0("Total Claims: ", n_claims),
            size = 5
        ) 
}

# data with one title per paper
df_titles <- df %>% 
    select(similar_title, S0_1Q1P2) %>% 
    group_by(similar_title) %>% 
    slice(1)

# Distribution of paper-level scores
df_app1 <- df_app %>% 
    group_by(similar_title, reproduction_id, claims, diname) %>%      #agg at repro-claim-di level (min? max? median? it should not matter)
    summarize(claim_di_level = mean(score)) %>% 
    ungroup(diname) %>% 
    summarise(claim_level_min = min(claim_di_level), 
              claim_level_max = max(claim_di_level), 
              claim_level_median = median(claim_di_level), 
              claim_level_mean = mean(claim_di_level)) %>%     #repro-claim level (min? max? median? across DIs)
    ungroup(claims) %>% 
    summarize(repro_level_min_min = min(claim_level_min),
              repro_level_max_max = max(claim_level_max),
              repro_level_med_med = median(claim_level_median),
              repro_level_mean_mean = mean(claim_level_mean),
              n_claims = n()) %>%   #repro-paper level (min? max? median? across claims)
    ungroup(reproduction_id) %>% 
    summarise(paper_level_min_min = mean(repro_level_min_min), 
              paper_level_max_max = mean(repro_level_max_max), 
              paper_level_med_med = mean(repro_level_med_med), 
              paper_level_mean_mean = mean(repro_level_mean_mean), 
              paper_level_sd = sd(repro_level_mean_mean), 
              n_repros = n(), 
              mean_n_claims = mean(n_claims)) %>% 
    left_join(df_titles, by = "similar_title") %>% group_by(similar_title) %>%
    arrange(paper_level_mean_mean) 



        df_app1 %>% ggplot(aes(x = paper_level_mean_mean)) + 
            geom_histogram(binwidth = 1, color="black", fill="gray") +
            labs(title = "Distribution of Reproduction Scores: Paper Level", 
                 x = "Reproducibility Score", 
                 y = "Count") +
            coord_cartesian(ylim =  c( 0, 5 )) +
            scale_x_continuous(breaks=1:10)

```

