---
title: "Reproducibility Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(tidyverse)
library(stringdist)       
library(readr)
library(viridisLite)
library(highcharter)
library(plotly)

df_app <- read_csv("test.csv")
```


Column 
------------------------------------------------------------------------
### Reproductions

```{r asd}
reproductions <- length(unique(df_app$repro_id))
valueBox(reproductions, icon = "fa-pencil")
```

### Papers

```{r asd1}
papers <-  length(unique(df_app$similar_title))
valueBox(papers, icon = "fa-file")
```



Row {data-height=500}
-----------------------------------------------------------------------

### 

```{r}
# - aggregate all obs at the claim-di level
# - aggregate at the claim level by taking the average of display item (one per di)
# - aggregate at the reproduction level by taking the average of claims (one per claim)
# - aggregate at the paper level by taking the average of reproduction (one per repro)


stat1 <- df_app %>% 
    group_by(similar_title, repro_id, claims, diname) %>%      #repro-claim-di level (min? max? median? it should not matter)
    summarize(claim_di_level = mean(score)) %>% 
    ungroup(diname) %>% 
    summarise(claim_level = mean(claim_di_level)) %>%  #repro-claim level (min? max? median?)
    ungroup(claims) %>% 
    summarize(repro_level = mean(claim_level)) %>% 
    ungroup(repro_id) %>% 
    summarise(paper_level = mean(repro_level))        #repro level 



stat1 %>% ggplot(aes(x = paper_level)) +
  geom_histogram(binwidth = 1,
                 color = "black",
                 fill = "gray") +
  labs(title = "Distribution of Reproduction Scores: Paper Level",
       x = "Reproducibility Score",
       y = "Count") +
  coord_cartesian(ylim =  c(0, 5)) +
  scale_x_continuous(breaks = 1:10)
```

### Description

Since its launch, in August 2021, the Social Science Reproduction Platform (SSRP) has help 
XXXX students and researchers around the world record the result of their reproductions in a standardized way. 
As part of their exercise, this reproducers have assessed a total of XXXX papers, and a total of YYYYY claims. This reproductions have also generate XXXXX improvements and YYYYY new robustness tests.  



Row {data-height=500}
-----------------------------------------------------------------------

### Reproducers Around the World 



```{r,   fig_width = 10, fig_height = 3.8, fig_retina = 2}
library(rnaturalearth)
library(rgeos)
world <- ne_countries(returnclass = "sf")
#> [1] "sf"    "data.frame"
testdata <- data.frame(admin = world$admin,
                       nreproductions = c(rep(0,29),
                                          2, # 2 Chile reproductions
                                          rep(0,138),
                                          5, # 5 US reproductions
                                          rep(0,8)))

plot_ly(world,type = 'choropleth', locations = world$adm0_a3,
        color = I("gray90"), stroke = I("black"), span = I(1)) %>%
  add_trace(z = testdata$nreproductions, colorscale="YlGnBu", reversescale=T)
```