---
title: "Reproducibility Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(tidyverse)
library(stringdist)       
library(readr)
library(viridisLite)
library(highcharter)
library(plotly)

df_app <- read_csv("test.csv")
```

## Column

### Reproductions

```{r asd}
reproductions <- length(unique(df_app$reproduction_id))
valueBox(reproductions, icon = "fa-pencil")
```

### Papers

```{r asd1}
papers <-  length(unique(df_app$similar_title))
valueBox(papers, icon = "fa-file")

claims <- df_app %>% mutate("claim_id" = paste0(similar_title, claims)) %>% summarise( length( unique(claim_id)) ) %>% as.numeric()
```

## Row {data-height="500"}

### Levels of Reproducibility
```{r}
# - aggregate all obs at the claim-di level
# - aggregate at the claim level by taking the average of display item (one per di)
# - aggregate at the reproduction level by taking the average of claims (one per claim)
# - aggregate at the paper level by taking the average of reproduction (one per repro)
stat1 <- df_app %>% 
    group_by(similar_title, reproduction_id, claims, diname) %>%      #repro-claim-di level (min? max? median? it should not matter)
    summarize(claim_di_level = mean(score)) %>% 
    ungroup(diname) %>% 
    summarise(claim_level = mean(claim_di_level)) %>%  #repro-claim level (min? max? median?)
    ungroup(claims) %>% 
    summarize(repro_level = mean(claim_level)) %>% 
    ungroup(reproduction_id) %>% 
    summarise(paper_level = mean(repro_level))        #repro level 
stat1 %>% ggplot(aes(x = paper_level)) +
  geom_histogram(binwidth = 1,
                 color = "black",
                 fill = "gray") +
  labs(title = "Distribution of Reproduction Scores: Paper Level",
       x = "Reproducibility Score",
       y = "Count") +
  coord_cartesian(ylim =  c(0, 25)) +
  scale_x_continuous(breaks = 1:10)
```


### Summary of Levels

| Level | Short summary                      |
|:-----:|:----------------------------------:|
| 1     | No Data or Code                    |
| 2     | Only Code                          |
| 3     | Partial analysis data & code       |
| 4     | All analysis data & code           |
| 5     | Reproducible from analysis data    |
| 6     | All cleaning code + L4             |
| 7     | Some raw data     + L6             |
| 8     | All cleaning code and raw data     |
| 9     | Reproducible from analysis  + L8   |
| 10    | Reproducible from raw data         |


### Description

This dashboard shows summary statistics of `r reproductions` reproductions recorded on the Social Science Reproduction Platform (SSRP) by students and researchers around the world. SSRP users have reproduced `r papers` papers and `r claims` claims. 

## Row {data-height="500"}

### Reproducers Around the World

```{r map,   fig_width = 10, fig_height = 3.8, fig_retina = 2}
library(rnaturalearth)
library(rgeos)

#get number of reproductions by country
country_counts <- df_app %>% 
  group_by(reproduction_id) %>% 
  slice(1) %>%
  group_by(country_code) %>% 
  count %>% 
  rename(postal = country_code)

world <- ne_countries(returnclass = "sf")
#merge to the world data 
world <- left_join(world, country_counts, by=c("postal")) %>% 
  mutate(n =  ifelse(is.na(n), 0, n))

testdata <- data.frame(admin = world$admin,
                       nreproductions = world$n
                       )

plot_ly(world,type = 'choropleth', locations = world$adm0_a3,
        color = I("gray90"), stroke = I("black"), span = I(1)) %>%
  add_trace(z = testdata$nreproductions, colorscale="YlGnBu", reversescale=T)
```


<!--
### Universities  

| University | Number of Reproductions |
|:-------------------:|:------:|
| UC Berkeley         | `r reproductions`      |
|                     |        |
|                     |        |

-->


